Job Demands-Resources model components through the lens of O*NET classifications

### 2021-12-09 Submission.Rmd
initial repo creation
Intro editing...

In an attempt to integrate the O\*NET taxonomy within the orientation of the Job Demands-Resources  [@demerouti2001job; @bakker2003dual; @bakker2017job], a series of evaluations were made that used: 1) O\*NET terminology (both descriptor and response option), 2) JD-R influenced ratings of demand, challenge, or hindrance. The outcome of this integration is a cross-walk between the Department of Labor classifications and the I-O literature steeped JD-R. While O\*Net provides thorough documentation of information associated with job analyses, one of the remaining limitations is its lack of connection to theory. Given the popularity of the Job Demands-Resources Theory [JD-R; @demerouti2001job] in exploring questions related to everything from motivation to job design, we aim to explore the intersection between perceptions of job demands and resources, and the broad set of job characteristics provided on O\*Net. In an attempt to integrate the O\*Net taxonomy within the orientation of the JD-R framework [@demerouti2001job; @bakker2003dual; @bakker2017job], a series of evaluations were made that used: 1) direct O\*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance. Prior to a description of results, a brief overview of both the JD-R theory and O\*Net is provided.

@@

@@

Interestingly, we have not yet integrated this practical and accessible resource within the JD-R framework. This paper aims to provide such a crosswalk or integration of the theory and practical occupations-focused data on O\*Net. Several broad research questions are examined across jobs:

@@

## ALTERNATIVELY, Alicia's JDR vs stress model predictions

Objective vs. Subjective Nature of Demands and Resources: The Role of Appraisal

>>>>

Given the popularity of the Job Demands-Resources Theory [JD-R; @demerouti2001job] in exploring questions related to everything from motivation to job design, we aim to explore the intersection between perceptions of job demands and resources, and the broad set of job characteristics provided on O\*Net. A series of evaluations were made that used: 1) direct O\*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance. Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O\*Net is provided.

@@

## Objective vs. Subjective Nature of Demands and Resources: The Role of Appraisal

@@

This paper aims to provide an integration of the theory and practical occupations-focused data on O\*Net. Several broad research questions are examined across jobs:

@@
